A high-repetition-rate, fast temperature-programmed gas chromatograph and its on-line coupling to a supercritical fluid chromatograph (SFC×GC)

### 2020-02-03 document.tex
Edits text to link to integrated multimedia.

The coaxial heater was made of a \SI{940}{\milli\metre} length of stainless
steel (SAE 304 grade), obtained from MIFAM (Milanówek, Poland). It had an
outside diameter of \SI{1.06}{\milli\metre} and an inside diameter of
\SI{0.80}{\milli\metre}. The ends of the coaxial heater tube terminated in two
identical, specially designed T-piece blocks, machined from brass (See Figure
\ref{fig:Manifold}). These blocks fulfilled three roles:
They (1) sealed the coaxial tube to contain coolant, (2) allowed electrical
connection to the coaxial heater, and (3) acted as a heated transfer line
between the column and the detector and inlet. Each end of the stainless-steel
tube of the coaxial heater was brazed onto a block. The CO$_2$ coolant passed
through one side, and on the opposite side a thermocouple probe inserted into a
blind hole measured the temperature of the block. An electrical contact was
added, to which an electrical conductor could be soft-soldered. Four holes
through the width of the block allowed the fitting of four \SI{220}{\volt},
\SI{100}{\watt} heater cartridges (Hotset), providing each of the two blocks
\SI{400}{\watt} of heating.  The chromatographic capillary column entered the
T-piece block via the bottom port with the coaxial heater tube and passed out
through the top port, where a micro-union using a metal ferrule
(Restek\texttrademark{} SilTite $\mu$-Union Connectors) brazed to the block
created a seal to contain the coolant. From the top port the the column crossed
a small, electrically isolating air gap before entering the inlet or detector.

@@

The resistance of the reference resistor ($R_{ref}$) was about \SI{0.005}{\ohm},
the resistance of the coaxial heater ($R_{col}$) was about  \SI{0.3}{\ohm}, and
the resistance of the ballast resistor was about \SI{0.01}{\ohm}, so that most
of the heat in the circuit was dissipated by the coaxial heater.
The potential differences across the coaxial heater ($V_{col}$) and the
reference resistor ($V_{ref}$) were measured (See Figure \ref{fig:Circuit}). If the
resistances of the coaxial heater and the reference resistor were both constant,
the ratio $V_{col}/V_{ref}$ would be constant, independent of the current.
But metals have positive coefficients of resistivity so the resistance of the
coaxial heater will increase with temperature. If the assumption is made that
the temperature of the reference resistor does not change, then the ratio
$V_{col}/V_{ref}$ will be proportional to $R_{col}$. If the resistance $R_{col}$
is assumed to be a monotonically rising function of the temperature ($R_{col} =
f(T)$), then the inverse function will provide the temperature ($T =
f^{-1}(R_{col})$). In practice the voltage $V_{ref}$ is too small to be
digitized directly and needs to be amplified to $V_b$, but it can be shown that
$R_{col}$ is a function of $\left(\frac{dV}{V_b}\right)$, where $dV$ is the
difference between the supply voltage and $V_b$. $dV$ and $V_b$ are of
magnitudes that can be conveniently digitized.

@@

As a first step in developing the coaxial heater, we tried to answer the
question about its temperature uniformity. Because the temperature coefficient
of resistivity of metals is positive, in the absence of equalizing heat flow
along the length of conductor the resistive heating process in a long, thin tube
is inherently unstable. To monitor the temperature profile along its length we
acquired a thermographic video of the coaxial heater (See Supplementary Online
Material). The video shows that the coaxial heater heats and cools smoothly with
no run-away hot spots. A still image from the video is show in Figure
\ref{fig:ThermImg}.

@@

\begin{figure}
  \includegraphics[width=\textwidth]{1-16.pdf}%
  \caption{\label{fig:ThermImg} A frame from the thermographic video of the coaxial heater. There are no evident run-away hot spots.}%
\end{figure}

@@

The attainable heating rate is a function of power to the heater and of the
temperature required. (In the instrument presented here the power was limited by
the voltage output range of the DAC of the data acquisition board, and not by
the power of the heater.) We were able to maintain controlled heating rates of
\SI{2500}{\celsius\per\minute} up to \SI{400}{\celsius}, or up to \SI{4000}{\celsius\per\minute}
up to \SI{350}{\celsius} (See Figure \ref{fig:MaxHeatingRate}). The heating
rates attainable seem to be high enough for the most demanding fast gas
chromatography.

@@

\section*{Supplementary Material}

In the supplementary material we provide a thermographic video of the coaxial
heater heating and cooling, which demonstrates the even of heating of the
coaxial heater and its rapid cooling by evaporating carbon dioxide.

@@

  saw sensors},}\ }in\ \href {https://doi.org/10.1109/ULTSYM.1991.234175}

@@

  {title} {\enquote {\bibinfo {title} {Research progress of saw gas
  charomatography},}\ }in\ \href {https://doi.org/10.1109/SPAWDA.2014.6998526}

@@

  chromatography (ufgc) and chemometric methods: Extending astm d7798 to

@@

  {\bibinfo {title} {Fast b-spline curve fitting by l-{BFGS}},}\ }\href

>>>>

The coaxial heater was made of a \SI{940}{\milli\metre} length of stainless
steel (SAE 304 grade), obtained from MIFAM (Milanówek, Poland). It had an
outside diameter of \SI{1.06}{\milli\metre} and an inside diameter of
\SI{0.80}{\milli\metre}. The ends of the coaxial heater tube terminated in two
identical, specially designed T-piece blocks, machined from brass (see Figure
\ref{fig:Manifold}). These blocks fulfilled three roles:
They (1) sealed the coaxial tube to contain coolant, (2) allowed electrical
connection to the coaxial heater, and (3) acted as a heated transfer line
between the column and the detector and inlet. Each end of the stainless-steel
tube of the coaxial heater was brazed onto a block. The CO$_2$ coolant passed
through one side, and on the opposite side a thermocouple probe inserted into a
blind hole measured the temperature of the block. An electrical contact was
added, to which an electrical conductor could be soft-soldered. Four holes
through the width of the block allowed the fitting of four \SI{220}{\volt},
\SI{100}{\watt} heater cartridges (Hotset), providing each of the two blocks
\SI{400}{\watt} of heating.  The chromatographic capillary column entered the
T-piece block via the bottom port with the coaxial heater tube and passed out
through the top port, where a micro-union using a metal ferrule
(Restek\texttrademark{} SilTite $\mu$-Union Connectors) brazed to the block
created a seal to contain the coolant. From the top port the the column crossed
a small, electrically isolating air gap before entering the inlet or detector.

@@

The resistance of the reference resistor ($R_{ref}$) was about \SI{0.005}{\ohm},
the resistance of the coaxial heater ($R_{col}$) was about  \SI{0.3}{\ohm}, and
the resistance of the ballast resistor was about \SI{0.01}{\ohm}, so that most
of the heat in the circuit was dissipated by the coaxial heater.
The potential differences across the coaxial heater ($V_{col}$) and the
reference resistor ($V_{ref}$) were measured (see Figure \ref{fig:Circuit}). If the
resistances of the coaxial heater and the reference resistor were both constant,
the ratio $V_{col}/V_{ref}$ would be constant, independent of the current.
But metals have positive coefficients of resistivity so the resistance of the
coaxial heater will increase with temperature. If the assumption is made that
the temperature of the reference resistor does not change, then the ratio
$V_{col}/V_{ref}$ will be proportional to $R_{col}$. If the resistance $R_{col}$
is assumed to be a monotonically rising function of the temperature ($R_{col} =
f(T)$), then the inverse function will provide the temperature ($T =
f^{-1}(R_{col})$). In practice the voltage $V_{ref}$ is too small to be
digitized directly and needs to be amplified to $V_b$, but it can be shown that
$R_{col}$ is a function of $\left(\frac{dV}{V_b}\right)$, where $dV$ is the
difference between the supply voltage and $V_b$. $dV$ and $V_b$ are of
magnitudes that can be conveniently digitized.

@@

As a first step in developing the coaxial heater, we tried to answer the
question about its temperature uniformity. Because the temperature coefficient
of resistivity of metals is positive, in the absence of equalizing heat flow
along the length of conductor the resistive heating process in a long, thin tube
is inherently unstable. To monitor the temperature profile along its length we
acquired a thermographic video of the coaxial heater. The video shows that the
coaxial heater heats and cools smoothly with no run-away hot spots, as shown in
Figure \ref{fig:ThermImg} (Multimedia view).

@@

\begin{figure}
  \includegraphics[width=\textwidth]{FLIR0111.pdf}%

  \caption{\label{fig:ThermImg} A frame from the thermographic video of the
  coaxial heater. There are no evident run-away hot spots. (Multimedia view)}%

@@

The attainable heating rate is a function of power to the heater and of the
temperature required. (In the instrument presented here the power was limited by
the voltage output range of the DAC of the data acquisition board, and not by
the power of the heater.) We were able to maintain controlled heating rates of
\SI{2500}{\celsius\per\minute} up to \SI{400}{\celsius}, or up to \SI{4000}{\celsius\per\minute}
up to \SI{350}{\celsius} (see Figure \ref{fig:MaxHeatingRate}). The heating
rates attainable seem to be high enough for the most demanding fast gas
chromatography.

@@

@@

  {SAW} sensors},}\ }in\ \href {https://doi.org/10.1109/ULTSYM.1991.234175}

@@

  {title} {\enquote {\bibinfo {title} {Research progress of {SAW} gas
  chromatography},}\ }in\ \href {https://doi.org/10.1109/SPAWDA.2014.6998526}

@@

  chromatography ({UFGC}) and chemometric methods: Extending {ASTM D7798} to

@@

  {\bibinfo {title} {Fast {B-spline} curve fitting by l-{BFGS}},}\ }\href
